---
output:
  md_document:
    variant: markdown_github
---

[![Coverage Status](https://img.shields.io/codecov/c/github/dirkschumacher/rpicosat/master.svg)](https://codecov.io/github/dirkschumacher/rpicosat?branch=master)
[![CRAN Status](http://www.r-pkg.org/badges/version/rpicosat)](https://CRAN.R-project.org/package=rpicosat)


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rpicosat

R bindings to the [PicoSAT solver release 965](http://fmv.jku.at/picosat/) by Armin Biere. The PicoSAT C code is distributed under a MIT style license and is bundled with this package.

## Install

### Install development version

```{r, eval=FALSE}
devtools::install_github("dirkschumacher/rpicosat")
```

### Install stable version from CRAN

```{r, eval = FALSE}
install.packages("rpicosat")
```


## API

* `picosat_sat` can solve a SAT problem. The result is a `data.frame` + meta data, so you can use it with `dplyr` et al.
* `picosat_solution_status` applied to the result of `picosat_sat` returns either *PICOSAT_SATISFIABLE*, *PICOSAT_UNSATISFIABLE* or *PICOSAT_UNKNOWN*

The following functions can be applied to solutions and make available some statistics generated by the `PicoSAT` solver:

* `picosat_added_original_clauses` #clauses
* `picosat_decisions` #decisions
* `picosat_propagations` #propagations
* `picosat_seconds` seconds spent in the C function `picosat_sat`
* `picosat_variables` #variables
* `picosat_visits` #visits

## Example

Suppose we want to test the following formula for satisfiability:


$$
(A \Rightarrow B)  \wedge (B \Rightarrow C) \wedge (C \Rightarrow A)
$$

This can be formulated as a CNF (conjunctive normal form):

$$
(\neg A \vee B)  \wedge (\neg B \vee C) \wedge (\neg C \vee A)
$$

In `rpicosat` the problem is encoded as a list of integer vectors.

```{r}
formula <- list(
  c(-1, 2),
  c(-2, 3),
  c(-3, 1)
)
```


```{r example}
library(rpicosat)
res <- picosat_sat(formula)
res
```

Every result is also a `data.frame` so you can process the results with packages like `dplyr`.

```{r}
as.data.frame(res)
```


We can also test for satisfiability if we assume that a certain literal is `TRUE` or `FALSE`

```{r}
picosat_sat(formula, c(1)) # assume A is TRUE
```

```{r}
picosat_sat(formula, c(1, -3)) # assume A is TRUE, but C is FALSE
```

## License

This R package is licensed under MIT. The PicoSAT solver bundled in this package is licensed MIT as well: Copyright (c) Armin Biere, Johannes Kepler University.

## Other packages

There are [numerous other packages](https://github.com/search?utf8=✓&q=picosat) providing bindings to PicoSAT. After writing this package I discovered [another package](https://github.com/dtimes6/Rpicosat) on github providing bindings to PicoSAT in R.

## Tests

```{r}
covr::package_coverage()
```

