---
output:
  md_document:
    variant: markdown_github
---
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/dirkschumacher/rpicosat?branch=master&svg=true)](https://ci.appveyor.com/project/dirkschumacher/rpicosat)
[![Travis-CI Build Status](https://travis-ci.org/dirkschumacher/rpicosat.svg?branch=master)](https://travis-ci.org/dirkschumacher/rpicosat)
[![Coverage Status](https://img.shields.io/codecov/c/github/dirkschumacher/rpicosat/master.svg)](https://codecov.io/github/dirkschumacher/rpicosat?branch=master)
[![CRAN Status](http://www.r-pkg.org/badges/version/rpicosat)](http://www.r-pkg.org/badges/version/rpicosat)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rpicosat

R bindings to the [PicoSAT solver release 965](http://fmv.jku.at/picosat/) by Armin Biere. The PicoSAT C code is distributed under a MIT style license and is bundled with this package.

## Install

```{r, eval=FALSE}
devtools::install_github("dirkschumacher/rpicosat")
```


## API

* `picosat_sat` can solve a SAT problem. The result is a tibble + meta data, so you can use it with `dplyr` et al.
* `picosat_solution_status` applied to the result of `picosat_sat` returns either `PICOSAT_SATISFIABLE`, `PICOSAT_UNSATISFIABLE` or `PICOSAT_UNKNOWN`

## Example

Suppose we want to test the following formula for satisfiability:


$$
(A \Rightarrow B)  \wedge (B \Rightarrow C) \wedge (C \Rightarrow A)
$$

This can be formulated as a CNF (conjunctive normal form):

$$
(\neg A \vee B)  \wedge (\neg B \vee C) \wedge (\neg C \vee A)
$$


```{r example}
library(rpicosat)
formula <- list(
  c(-1, 2),
  c(-2, 3),
  c(-3, 1)
)
picosat_sat(formula)
```

Every result is also a `tibble` so you can process the results with packages like `dplyr`.

We can also test for satisfiability if we assume that a certain literal is `TRUE` or `FALSE`

```{r}
picosat_sat(formula, c(1)) # assume A is TRUE
```

```{r}
picosat_sat(formula, c(1, -3)) # assume A is TRUE, but C is FALSE
```

